\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-05-02 ase20/eval.tex
[ASE] Footnotesize in Table 5
Minor edit

ES10-9 is due to multiple semantics.  While any tests in Test262 do not fail
with two different semantics, we could detect this error via {\sf Spec
Extractor} even before executing semantics. It is a supplementary merit of
the mechanization of IR-based semantics extraction.

@@

\footnotesize
    \scode{matchAll} of \scode{String} &
    0 &
    0 &
    9/9 &
    5/5 &
    \inred{XXXXX}/18,064\\\hline

    \scode{import()} &
    0 &
    2 &
    22/23 &
    0/0 &
    \inred{XXXXX}/18,064\\\hline

    \scode{BigInt} &
    4 &
    0 &
    258/323 &
    \inred{207}/207 &
    \inred{XXXXX}/18,064\\\hline

    \scode{Promise.allSettled } &
    0 &
    0 &
    79/85 &
    50/50 &
    \inred{XXXXX}/18,064\\\hline

    \scode{globalThis} &
    0 &
    0 &
    1/1 &
    1/1 &
    \inred{XXXXX}/18,064\\\hline

\footnotesize
    \scode{for-in}  mechanics &
    0 &
    0 &
    36/37 &
    0/0 &
    \inred{XXXXX}/18,064\\\hline

\footnotesize    Optional Chaining &
    3 &
    3 &
    72/74 &
    19/19 &
    \inred{XXXXX}/18,064\\\hline

\footnotesize   Nullish Coalescing Op. &
    1 &
    4 &
    10/10 &
    21/21 &
    \inred{XXXXX}/18,064\\\hline

    \scode{import.meta} &
    0 &
    2 &
    15/15 &
    0/0 &
    \inred{XXXXX}/18,064\\\hline

>>>>

ES10-9 is due to multiple semantics.  While no tests in Test262 fail
with any of the semantics, we could detect this error via {\sf Spec
Extractor} even before executing the semantics. It is supplementary merit of
the mechanization of IR-based semantics extraction.

@@

    \code{matchAll} of \code{String} &
    0 &
    0 &
    9/9 &
    5/5 &
    18,064/18,064\\\hline

    \code{import()} &
    0 &
    2 &
    22/23 &
    0/0 &
    18,064/18,064\\\hline

    \code{BigInt} &
    4 &
    0 &
    258/323 &
    \inred{207}/207 &
    \inred{18,064}/18,064\\\hline

    \code{Promise.allSettled } &
    0 &
    0 &
    79/85 &
    50/50 &
    18,064/18,064\\\hline

    \code{globalThis} &
    0 &
    0 &
    1/1 &
    1/1 &
    18,064/18,064\\\hline

    \code{for-in}  mechanics &
    0 &
    0 &
    36/37 &
    0/0 &
    18,064/18,064\\\hline

    Optional Chaining &
    3 &
    3 &
    72/74 &
    19/19 &
    18,064/18,064\\\hline

    Nullish Coalescing Op. &
    1 &
    4 &
    10/10 &
    21/21 &
    18,064/18,064\\\hline

    \code{import.meta} &
    0 &
    2 &
    15/15 &
    0/0 &
    18,064/18,064\\\hline
